### 2023-11-13 Data/AnalysisData/codebook_plot_46_data_REV.Rmd
added the results for H5 and H6, including plot 46, which also required the adition of the plot_46_data_rev file, which lead to a rerun of the final data creation code.

---
title: "Codebook created on 2023-11-13 at 2023-11-13 11:23:30.376704"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_Plot_46_data.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-13 at 2023-11-13 11:23:32.03741"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_plot_46_data_REV.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-13 Scripts/Manuscript/manuscript.Rmd
added the results for H5 and H6, including plot 46, which also required the adition of the plot_46_data_rev file, which lead to a rerun of the final data creation code.

## graphs
# plot accompanying the results for Hypotheses 4, 5, & 6.
plot_456_data <- data_prep_plot_456(data_h6)
# plot accompanying the results for Hypotheses 4, & 6
Plot_46_data <- data_prep_plot_46(data_h6[c(3, 6, 9, 12, 15, 36, 39, 42, 45, 48)])
# plot accompanying the results for Hypotheses 2, & 3
plot_23_data_alpha <- data_prep_plot_23_alpha(data_h3_multiple)
plot_23_data_omega <- data_prep_plot_23_omega(data_h3_multiple)

@@

open_data(data = Plot_46_data, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(Plot_46_data))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(Plot_46_data))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(Plot_46_data))), ".yml"))

@@

check_h5 <- lmer(formula = QMP ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens)
H5_sensitivity_test_results <- summary(check_h5)$coefficients

check_h5_REV <- lmer(formula = QMP_REV ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens)
H5_sensitivity_test_results_REV <- summary(check_h5_REV)$coefficients

@@

# running the models one with none revised QMP ratio's and one with
check_h6 <- lmer(formula = Rep_QMP ~ 1 + QMP + (1|many_labs_version), data = data_h6_sens)
H6_sensitivity_test_results <- summary(check_h6)$coefficients

check_h6_REV <- lmer(formula = Rep_QMP_REV ~ 1 + QMP_REV + (1|many_labs_version), data = data_h6_sens)
H6_sensitivity_test_results_REV <- summary(check_h6_REV)$coefficients

# n of mod ratio's pressent check
H6_n_check_results <- betareg(Rep_op_ratio ~ mod_ratio, data = data_h6)$n
H6_n_check_results_REV <- betareg(Rep_op_REV_ratio ~ mod_REV_ratio, data = data_h6)$n

@@

INSERT HERE 256

@@

@@

@@

A similar beta-regression tested the association between replication success and QMP ratio in replication protocols. Results showed that successful replication significantly related to a decrease in the ratio of QMPs in replication protocols $\left(B = -0.588, SD = 0.212, p < .001 \right)$. Sensitivity analyses were performed using a random-intercept multilevel regression function. This model also found a significant association between replication success and QMP ratio $\left(B = -0.963, t(70.319) = -1.491, p = .011 \right)$. Both of these results are in line with hypothesis 5. However, the relationship in the multilevel model is no longer significant for QMP ratios obtained with the initial coding protocol $\left(B = -0.517, t(63.122) = -2.635, p = .140 \right)$.

The relation between QMP ratios in the replication protocols and corresponding original articles were investigated using a beta regression model. It showed that total QMP ratio in the original article can significantly predict total QMP ratio in the subsequent replication ($B = 1.477, SD = 0.579, p < .001$), which provides some evidence in favor of hypothesis 6. However, this relation was not significant for the QMP ratios obtained with the initial protocol ($B = -0.387, SD = 0.511, p = 0.449$). Sensitivity analyses using a random intercept logistic multilevel model also found similar discrepancy in results between revised and initial protocol (revised protocol: $B = 0.249, t(74.473) = 1.498, p < 0.001$; initial protocol $B = -0.057, t(74.620) = -0.332, p = 0.741$).

INSERT FIGURE 26 HERE

>>>>

## graphs
# plot accompanying the results for Hypotheses 4, 5, & 6.
plot_456_data <- data_prep_plot_456(data_h6)
# plot accompanying the results for Hypotheses 4, & 6
plot_46_data <- data_prep_plot_46(data_h6[c(3, 6, 9, 12, 15, 36, 39, 42, 45, 48)])
plot_46_data_rev <- data_prep_plot_46(data_h6[c(3, 21, 24, 27, 30, 36, 54, 57, 60, 63)])
# plot accompanying the results for Hypotheses 2, & 3
plot_23_data_alpha <- data_prep_plot_23_alpha(data_h3_multiple)
plot_23_data_omega <- data_prep_plot_23_omega(data_h3_multiple)

@@

open_data(data = plot_46_data, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(Plot_46_data))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(Plot_46_data))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(Plot_46_data))), ".yml"))

open_data(data = plot_46_data_rev, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(plot_46_data_rev))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(plot_46_data_rev))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(plot_46_data_rev))), ".yml"))

@@

check_h5 <- apa_print(lmer(formula = QMP ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens))

check_h5_REV <- apa_print(lmer(formula = QMP_REV ~ 1 + hypothesis_support + (1|many_labs_version), data = data_h5_sens))

@@

# running the models one with none revised QMP ratio's and one with
check_h6 <- apa_print(lmer(formula = Rep_QMP ~ 1 + QMP + (1|many_labs_version), data = data_h6_sens))

check_h6_REV <- apa_print(lmer(formula = Rep_QMP_REV ~ 1 + QMP_REV + (1|many_labs_version), data = data_h6_sens))

# n of mod ratio's that are present (check)
H6_n_check_results <- betareg(Rep_op_ratio ~ mod_ratio, data = data_h6)$n
H6_n_check_results_REV <- betareg(Rep_op_REV_ratio ~ mod_REV_ratio, data = data_h6)$n

@@

@@

A similar beta-regression tested the association between replication success and QMP ratio in replication protocols. Results showed that successful replication significantly related to a decrease in the ratio of QMPs in replication protocols (`r betareg_output_to_apa_full(H5_test_results_REV)`). Sensitivity analyses were performed using a random-intercept multilevel regression function. This model also found a significant association between replication success and QMP ratio (`r check_h5_REV$full_result$hypothesis_supportTRUE`). Both of these results are in line with hypothesis 5. However, the relationship in the multilevel model is no longer significant for QMP ratios obtained with the initial coding protocol (`r check_h5$full_result$hypothesis_supportTRUE`).

The relation between QMP ratios in the replication protocols and corresponding original articles were investigated using a beta regression model. It showed that total QMP ratio in the original article can significantly predict total QMP ratio in the subsequent replication (`r betareg_output_to_apa_full(H6_test_results_REV)`), which provides some evidence in favor of hypothesis 6. However, this relation was not significant for the QMP ratios obtained with the initial protocol (`r betareg_output_to_apa_full(H6_test_results)`). Sensitivity analyses using a random intercept logistic multilevel model also found some discrepancy in results between revised and initial protocol, albeit with both being non-significant (revised protocol: `r check_h6_REV$full_result$QMP_REV`; initial protocol `r check_h6$full_result$QMP`).

INSERT FIGURE 46 HERE

```{r Plot 46 Initial Data Code, include = FALSE, eval = FALSE}
# Initial
ggplot(plot_46_data, aes(QMP_ratio, QMP_Rep_ratio)) + 
  geom_point() +
  geom_jitter(width = 0.05, height = 0.05) +
  stat_smooth(method="lm") + 
  theme_bw() +
  theme(strip.text.y = element_text(size = 7), strip.background = element_rect(
    color = "black", fill = "white", size = 1, linetype = "solid"
  )) +
  xlab("QMP Ratio (Original)") + ylab("QMP Ratio (Replication)") +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1")) + 
  facet_grid(vars(QMP_Rep_type), vars(QMP_type))

1
```{r Plot 46 Revised Data Code}
# Revised
ggplot(plot_46_data_rev, aes(QMP_ratio, QMP_Rep_ratio)) + 
  geom_point() +
  geom_jitter(width = 0.05, height = 0.05) +
  stat_smooth(method="lm") + 
  theme_bw() +
  theme(strip.text.y = element_text(size = 7), strip.background = element_rect(
    color = "black", fill = "white", size = 1, linetype = "solid"
  )) +
  xlab("QMP Ratio (Original)") + ylab("QMP Ratio (Replication)") +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1")) + 
  facet_grid(vars(QMP_Rep_type), vars(QMP_type))

@@

# $\left(B = -0.963, t(70.319) = -1.491, p = .011 \right)$

@@
